RStudio Intro - IASSIST Reproducible R Workshop
========================================================

### Installation

Requirements for the course:

R - 
Rstudio - 
Git 

If you don't want to install this on your machine, we've installed a version of RStudio server on our server.  Harrison can give you an account. 

### Quick note about R (more to come later)

R is an interactive statistical computing programming laguage in the read–eval–print loop (REPL) style where: 

* read user types command in console prompt
* the command is **eval**uated
* the result is printed to the console 
* and loop expresses the iterative and exploratory nature of how someone uses r in practice

### Setups for RStudio

We need to grab some rcode for this section, so let's create a new project Project>Create Project>Version Control

repo url: git@github.com:uc-data-services/r-reproducible-research.git
director: r-iassist  (can be whatever you want)
folder: leave as is or navigate to desktop or my docs

screenshot?

things to show for step one: 
1. setting working director
2. show git menu in workspace area
3. show files


## Step 2 - open r file run code

1. open file x 
2. notice source edit area, hihglight line and run
3. poss run somethign that requires a pakcage not installed, install and run again
4. ways to get help
5. show tab and tooltip 


## Plots area and typing into console 

```{r}
summary(mtcars)
```

You can also embed plots, for example:

```{r fig.width=7, fig.height=6}
plot(mtcars$mgp, mtcars$wt)
```

